% !TEX program = xelatex
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
\documentclass[12pt, a4paper]{awesome-cv}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
\fontdir[fonts/]
\colorlet{awesome}{awesome-red}
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}
% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo{./examples/profile.png}
\name{William}{Kane}
\position{Graduate {\enskip\cdotp\enskip} Curriculum Vitae}
\address{Wrexham / Liverpool}
\mobile{: 07475767472}
\email{: billy.kanee@gmail.com}
%\homepage{tubestubes.github.io}
\github{GitHub: tubestubes}
\linkedin{ LinkedIn: william-kane-004436170}
%\gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

\quote{More details can be found on my online CV at tubestubes.github.io}

%-------------------------------------------------------------------------------
%   HEADER AND FOOTER
%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed

\makecvfooter
  {\today}
  {William Kane~~~·~~~Curriculum Vitae}
  {\thepage}

%-------------------------------------------------------------------------------
%	Body
%-------------------------------------------------------------------------------
\cvsection{Summary}

\begin{cvparagraph}
New graduate with a focus on data analysis, statistics, mathematics, and python. Looking to hit the ground running and start a career in Cheshire. Suited to data analysis roles with routes for progression. My career goal is to take responsibility for data modelling and analysis at a senior or managerial level, using the latest data science techniques, work-flows, and intelligent automated systems. Keen to engage, learn, and work at a fast pace.
\end{cvparagraph}

%---------------------------------------------------------
\cvsection{Skills}
\begin{cvskills}

  \cvskill
    {Mathematics} % Category
    {Statistics (with Bayesian), Modelling, Optimisation, Numerical Methods, Maple} % Skills

  \cvskill
    {Python} % Category
    {Data Science, Spatial Data Science, OOP, Jupyter, Agent-Based Modelling, Machine Learning, Data Mining } % Skills

  \cvskill
    {Software} % Category
    {SQL, R/RStudio, Julia, Maple, MATLAB, Microsoft Office, LaTeX, Git/GitHub with Git Bash, Docker, Ubuntu} % Skills
    
  \cvskill
    {Professional} % Category
    {Leadership, Life-long Learning, Team Work, Project Leadership, Communication and Presentation, Time Management, Prioritisation } % Skills

\end{cvskills}

%---------------------------------------------------------
\cvsection{Education}
\begin{cventries}

  \cventry
    {University of Liverpool} % Institution
    {MSc(Eng) in Risk and Uncertainty} % Degree
    {Distinction} % Location
    {Sept. 2019 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{\textbf{Modules include} Modern Management, Geographic Data Science, Data Mining, Monte Carlo, Risk Analysis}
        \item{\textbf{Research project in} Agent-based modelling of mixed autonomous/human vehicles in a road network}
        \item{Other projects include training an artificial neural network to act as a surrogate model in python, and advanced Monte Carlo methods in MATLAB.}
      	\item{This course built on technical knowledge of Bachelors degree and focused on a deeper understanding of key concepts. I split my focus 50:50 between data science orientated and risk orientated modules, as well as general modules on Advanced Modern Management and Project Planning. The course concluded with a three month research project in which I developed object orientated python code to simulate the effects of driverless cars mixed with normal traffic on traffic flow, and wrote up a detailed analysis of the data I generated.}
        \item{The skills developed in this degree built on what I had before while teaching me to work independently with minimal guidance, and to carefully plan and manage my ongoing projects to deliver each one on time without comprising quality. I also gained valuable technical knowledge in data analysis, data science, machine learning, and programming to be used in the future. } 
      \end{cvitems}
    }

  \cventry
    {University of Liverpool} % Institution
    {BSc in Mathematics} % Degree
    {2:1} % Location
    {Sept. 2016 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{\textbf{Modules include} Statistics, Calculus, Modelling, Quantum Mechanics, Networks, Finance, Game Theory / Economics, Operational Research}
        \item{\textbf{Group Project} where I lead and coordinated  my group to create a report on using Maple for operational research calculations.}
        \item{Throughout this course I developed sharp skills in the foundations of mathematics, statistics, problem solving, numerical methods, and scientific computing. I focused on applied modules, always learning how mathematical models can be used on important problems. Managing the high workload matured my skills in time management and self motivation key to success in the workplace.}
      \end{cvitems}
    }
    
\cventry
    {Coleg Cambria Yale} % Institution
    {A Levels} % Degree
    {A*AAB} % Location
    {Sept. 2013 - Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{A Levels} Mathematics (A*), Further Mathematics (A), Physics (A), Chemistry (B)}
      \end{cvitems}
    }

\cventry
    {Darland High School} % Institution
    {GCSEs} % Degree
    { } % Location
    {Sept. 2008 - Jun. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
		\item{\textbf{ 9 GCSEs including} English (A*), Systems and Control (A), Media Studies (A*)}
      \end{cvitems}
    }

\end{cventries}
%---------------------------------------------------------
\newpage
%---------------------------------------------------------
\cvsection{Experience}
\begin{cventries}

  \cventry
    {Bar Tender} % Job title
    {Soho Bar} % Organization
    {Liverpool} % Location
    {Jun. 2018 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{\textbf{Skills developed:} Customer Service, Delivering at Page, Managing a Quality Service, Teamwork}
        \item {A fast paced and customer focused job where I developed skills in hospitality which can be transferred to other situations involving solving problems on the fly to provide clients with what they expect.}
      \end{cvitems}
	}

  \cventry
    {Tuition Assistant} % Job title
    {KUMON} % Organization
    {Wrexham} % Location
    {Sept. 2013 - Oct. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{\textbf{Skills developed:} Communication and Presentation, Team Work, Supporting Others}
        \item {Tuition provided me an excellent opportunity to work with people and help them learn and develop their skills in maths and English. A satisfying job and one that taught me a lot about dealing with people and how to communicate clearly and affectively.}
      \end{cvitems}
    }

\end{cventries}

%---------------------------------------------------------
%\newpage
%---------------------------------------------------------
\cvsection{Side Projects}
\begin{cventries}

  \cventry
    {Interactive visualisation of the data outputted from my masters' simulation} % Sub title
    {R Shiny Dashboard} % Main title
    {} % rhs red
    {} % rhs sub
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{\textbf{Skills developed:} Interactive visualisation, Data Dashboards, R, R Shiny}
        \item{To learn the ropes of R Shiny and creating dashboards, I developed an interative web interface to visualise data from the various simulations I ran while collecting data in for my masters' dissertation.}
      \end{cvitems}
	}

  \cventry
    {Github pages website created with R Markdown} % Sub title
    {Personal Website} % Main title
    {} % rhs red
    {} % rhs sub
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{\textbf{Skills developed:} R, R Markdown, Basic Web Development}
        \item{I developed a minimalist website to function as an online CV, hosted on Github Pages. I used this to learn the ropes of R Markdown}
      \end{cvitems}
	}

  \cventry
    {Jekyll website hosted on GitHib Pages} % Sub title
    {Local Business Website} % Main title
    {} % rhs red
    {} % rhs sub
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{\textbf{Skills developed:} Basic Web Development, R, SEO}
        \item{I used Jeykll to create a simple static website for a new local business.}
      \end{cvitems}
	}

\end{cventries}

%---------------------------------------------------------
\cvsection{Achievements}
\begin{cvhonors}

  \cvhonor
    {Charitable Work} % Award
    {Operation Christmas Child} % Event
    {Wrexham} % Location
    {2013} % Date(s)
  
  \cvhonor
    {Duke of Edinburgh's Award} % Award
    {Silver} % Event
    {Wrexham} % Location
    {2013} % Date(s)

\cvhonor
    {First Aid} % Award
    {Basic qualification} % Event
    {Wrexham} % Location
    {2012} % Date(s)
    
\cvhonor
    {Black Belt} % Award
    {Tae-Kwon-Do } % Event
    {Wrexham} % Location
    {2012} % Date(s)

\end{cvhonors}

%---------------------------------------------------------
\cvsection{References}
\begin{cventries}

  \cventry
    {Master's Project Supervisor} 
    {Dr Hongbo Ye}
    { }
    { }
    {
      \begin{cvitems}
        \item {Hongbo.Ye@liverpool.ac.uk}
      \end{cvitems}
	}

  \cventry
    {BSc Academic Adviser} % Subtitle
    {Professor Ke Chen} %Title
    { } % Red RHS
    { } % Grey RHS
    {
      \begin{cvitems}
        \item {cmchenke@liverpool.ac.uk}
      \end{cvitems}
	}

  \cventry
    {MSc(Eng) Department head} 
    {Professor Scott Ferson} 
    { } 
    { } 
    {
      \begin{cvitems} 
        \item {ferson@liverpool.ac.uk}
      \end{cvitems}
	}

\end{cventries}

%-------------------------------------------------------------------------------
\end{document}
