%-------------------------------------------------------------------------------
%	EDUCATION
%-------------------------------------------------------------------------------
\cvsection{Education}
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {University of Liverpool} % Institution
    {MSc(Eng) in Risk and Uncertainty} % Degree
    {Graduate Aug 2020} % Location
    {Sept. 2019 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Modules include} Modern Management, Geographic Data Science, Data Mining, Monte Carlo, Risk Analysis}
        \item {\textbf{Research project in} Agent-based modelling of mixed autonomous/human vehicles in a road network}
        \item {Other projects include training an artificial neural network to act as a surrogate model in python, and advanced Monte Carlo methods in MATLAB.}
	\item {This course built on technical knowledge of Bachelors degree and focused on a deeper understanding of key concepts. I split my focus 50:50 between data science orientated and risk orientated modules, as well as general modules on Advanced Modern Management and Project Planning. The course concluded with a three month research project in which I developed object orientated python code to simulate the effects of driverless cars mixed with normal traffic on traffic flow, and wrote up a detailed analysis of the data I generated.}
        \item {The skills developed in this degree built on what I had before while teaching me to work independently with minimal guidance, and to carefully plan and manage my ongoing projects to deliver each one on time without comprising quality. I also gained valuable technical knowledge in TOPIC to be used in the future. } 
      \end{cvitems}
    }

  \cventry
    {University of Liverpool} % Institution
    {BSc in Mathematics} % Degree
    {2:1} % Location
    {Sept. 2016 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Modules include} Statistics, Calculus, Modelling, Quantum Mechanics, Networks, Finance, Game Theory / Economics, Operational Research}
        \item \textbf{Group Project} where I lead and coordinated  my group to create a report on using Maple for operational research calculations.
        \item {Throughout this course I developed sharp skills in problem solving, numerical methods, and analysis. I focused on applied modules, always learning how mathematical models can be used on important problems. Managing the high workload matured my skills in time management and self motivation key to success in the workplace.}  
      \end{cvitems}
    }
    
\cventry
    {Coleg Cambria Yale} % Institution
    {A Levels} % Degree
    {A*AAB} % Location
    {Sept. 2013 - Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{A Levels} Mathematics (A*), Further Mathematics (A), Physics (A), Chemistry (B)}
      \end{cvitems}
    }

\cventry
    {Darland High School} % Institution
    {GCSEs} % Degree
    { } % Location
    {Sept. 2008 - Jun. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
		\item{\textbf{ 9 GCSEs including} English (A*), Systems and Control (A), Media Studies (A*)}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
